A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-24 tex/body.tex
minor

By Theorems~\ref{thm:t},~\ref{thm:rs}, and~\ref{thm:ss}, the
calculus is sound and complete for the universal $\thD$ theory. We can
rightly call it a decision procedure.

>>>>

By Theorems~\ref{thm:t},~\ref{thm:rs}, and~\ref{thm:ss}, the
calculus is sound and complete for the universal theory of (co)datatypes. We can
rightly call it a decision procedure for that theory.
